Mergeable Types

### 2017-02-28 paper/implementation.tex

Importantly, Irmin supports user-defined three-way merge functions for
reconciling concurrent operations. While Irmin's merge functions are
defined over objects on Irmin's content-addressable heap, \name's
merge functions are defined over OCaml types. We address this
representational mismatch with the help of OCaml's PPX metaprogramming
support~\cite{ppx} to derive bi-directional transformations between
objects on OCaml and Irmin heaps. We also derive the various
serialization functions required by Irmin\footnote{
  The Since \nameMonad monad relies on Irmin for realizing the branch
  structure, it is in fact parameterized over a mergeable type that
  implements all these functions. Thus the monad is functorized over
  the mergeable type, but not polymorphic. The convenience of type
  parameter inference that polymorphism offers can however be obtained
  for module parameters using OCaml extensioms, such as Modular
  Implicits~\cite{implicits}.
}.
Synchronization between replicas is performed using Git's notion of
pushing and pulling updates from remotes over the Git transfer
protocol~\cite{git-tp}. As a result, we reap the benefits of efficient
delta-transfer (only missing objects are transferred between
replicas), compression and end-to-end encrypted communication between
he replicas.

>>>>

Importantly, Irmin supports user-defined three-way merge functions for
reconciling concurrent operations. While Irmin's merge functions are
defined over objects on Irmin's content-addressable heap, \name's
merge functions are defined over OCaml types. We address this
representational mismatch with the help of OCaml's PPX metaprogramming
support~\cite{ppx} to derive bi-directional transformations between
objects on OCaml and Irmin heaps. We also derive the various
serialization functions required by Irmin\footnote{
  The Since \nameMonad monad relies on Irmin for realizing the branch
  structure, it is in fact parameterized over a mergeable type that
  implements all these functions. Thus the monad is functorized over
  the mergeable type, but not polymorphic. The convenience of type
  parameter inference that polymorphism offers can however be obtained
  for module parameters using OCaml extensioms, such as Modular
  Implicits~\cite{implicits}.
}.
Synchronization between replicas is performed using Git's notion of
pushing and pulling updates from remotes~\cite{git-tp}. As a result, we reap the
benefits of efficient delta-transfer (only missing objects are transferred between
replicas), compression and end-to-end encrypted communication between
the replicas.

### 2017-02-28 paper/related.tex

>>>>

\name uses 3-way merges using the lowest common ancestor, which is critical for
all of our user-defined merges. However, CRDTs do not have the benefit of
lowest common ancestor for merges and are only presented with the two
concurrent versions. If a 3-way merge is desired, then the causal history has
to be explicitly encoded in the data type. As a result, constructing even
simple data types like counters are more complicated using CRDTs~\cite{crdt}
compared to their implementation in \name. CRDTs also tend to be implemented
directly over the network protocols. Hence, low-level concerns such as
duplicate delivery, lost messages, message reordering are explicitly handled in
the data type definition. In \name, the programmer does not have to deal with
underlying network issues since \name is realized on Irmin, a high-level
branch-consistent distributed store.
